Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-14 aistats.tex
Finish gaussian section

\subsection{Gaussian}
\label{ssec:gaussian}
The ubiquitous Gaussian $\cN(m,\sigma^2)$ actually offers a highly non-trivial example for Problem 1.
Its log-likelihood reads $p(x) = -\frac{(x-m)^2}{2 \sigma^2} - \half \log(2\pi\sigma^2)$.
With sufficient statistic $T(x)=(x, x^2)$, 
the mean parameters are $\m = \E[T(X)] = (m , m^2 + \sigma^2)$ belonging to the open set $\cM= \{(u,v) \cond u^2 < v\}$,
and the natural parameters are $\nat= (\frac{m}{\sigma^2} , \frac{-1}{2\sigma^2}) \in \Theta = \real \times \real_-$. 
$\cM$ and $\Theta$ are delimited in grey in \cref{fig:thales}.
Given these parameters, log-partition and entropy are
\alignn{
	\logpart(\nat) &= \frac{\nat_1^2}{-4\nat_2} - \half \log(-2\nat_2) \\
	\conj(\m) &= - \half \log (\mu_2 - \mu_1^2)
}
up to constants.

 Neither its log-partition nor its entropy are smooth, strongly-convex, or self-concordant.

Equipped with the knowledge of these 2 examples, we are ready to discuss the general problem, and some ways to solve with direct expansions of the Bregman.

@@

>>>>

\subsection{Gaussian}
\label{ssec:gaussian}
Now that we have solved the case of $\cN(0,\sigma^2)$, let's move on to the ubiquitous Gaussian $\cN(m,\sigma^2)$.
Gaussians actually offers a highly non-trivial example for Problem 1.
Their log-likelihood reads $p(x) = -\frac{(x-m)^2}{2 \sigma^2} - \half \log(2\pi\sigma^2)$.
With sufficient statistic $T(x)=(x, x^2)$, 
the mean parameters are $\m = \E[T(X)] = (m , m^2 + \sigma^2)$ belonging to the open set $\cM= \{(u,v) \cond u^2 < v\}$,
and the natural parameters are $\nat= (\frac{m}{\sigma^2} , \frac{-1}{2\sigma^2}) \in \Theta = \real \times \real_-$. 
Examples of MAP and MLE  are represented in \cref{fig:thales} within $\cM$ and $\Theta$ delimited in grey.
Given these parameters, log-partition and entropy are, up to constants, 
\alignn{
	\logpart(\nat) &= \frac{\nat_1^2}{-4\nat_2} - \half \log(-2\nat_2) \\
	\conj(\m) &= - \half \log (\mu_2 - \mu_1^2)
}

These functions are neither smooth, nor strongly convex, nor self-concordant (see \cref{app:gaussian}).
Let us keep this in mind, as we move on to discussing the general problem, and some ways to solve it via direct expansions of the Bregman divergence.

@@

\section{PROOFS FOR GAUSSIAN}
\label{app:gaussian}
